---
title: "Autonomous Equity Research & Econometric Dossier"
author: "Antigravity Research Agents Committee & RStudio"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
source("agent_bridge.R")
```

# Executive Summary

This institutional research document combines **Google Antigravity Finance Agents** with **RStudio & R Econometric Modeling**.

- **Primary Source Filing:** Audited SEC Form 10-K / 20-F filings anchored strictly by Accession Number (`accn`).
- **Valuation Models:** Deterministic DCF, Elastic Reverse DCF Solver, and Vectorized Monte Carlo Simulations.
- **Provenance Integrity:** Every figure is verified by an independent Verifier against a tamper-evident HMAC-SHA256 ledger.

---

# Data Layer: Audited Financial Extraction

```{r fetch_fundamentals}
# Dynamically extract verified annual fundamental metrics
aapl_data <- fetch_sec_financials("AAPL")

cat(sprintf("Ticker: %s\n", aapl_data$ticker))
cat(sprintf("Source: %s\n", aapl_data$source))
cat(sprintf("Fiscal Period: %s (Period End: %s)\n", aapl_data$period, aapl_data$period_end))
cat(sprintf("Revenue: $%s\n", format(aapl_data$revenue, big.mark = ",")))
cat(sprintf("Operating Income: $%s\n", format(aapl_data$operating_income, big.mark = ",")))
cat(sprintf("Operating Cash Flow: $%s\n", format(aapl_data$operating_cash_flow, big.mark = ",")))
cat(sprintf("Free Cash Flow: $%s\n", format(aapl_data$operating_cash_flow - aapl_data$capex, big.mark = ",")))
```

---

# Deterministic Discounted Cash Flow (DCF) Valuation

```{r dcf_valuation}
# Compute DCF Fair Value using verified baseline Free Cash Flow
base_fcf <- (aapl_data$operating_cash_flow - aapl_data$capex)
shares_out <- 15.1e9 # Diluted shares outstanding
growth_projections <- c(0.08, 0.07, 0.06, 0.05, 0.04)

dcf_result <- calc_dcf(
  base_fcf = base_fcf,
  growth_rates = growth_projections,
  discount_rate = 0.088,
  terminal_growth_rate = 0.025,
  shares_outstanding = shares_out,
  net_debt = 0.0,
  mid_year = FALSE
)

cat(sprintf("DCF Fair Value per Share: %s\n", dcf_result$formatted))
cat(sprintf("Enterprise Value: $%s\n", format(dcf_result$result$enterprise_value, big.mark = ",")))
cat(sprintf("Present Value of Explicit FCFs: $%s\n", format(dcf_result$result$pv_explicit_fcf, big.mark = ",")))
cat(sprintf("Present Value of Terminal Value: $%s\n", format(dcf_result$result$pv_terminal_value, big.mark = ",")))
```

---

# Econometric Risk: Monte Carlo Valuation Simulation

Using native R statistical sampling to shock WACC and growth rates under regulatory bounds:

```{r monte_carlo}
mc_sim <- r_monte_carlo_dcf(
  base_fcf = base_fcf,
  shares_outstanding = shares_out,
  net_debt = 0.0,
  wacc_mean = 0.088,
  wacc_sd = 0.007,
  growth_mean = 0.06,
  growth_sd = 0.015,
  terminal_g = 0.025,
  n_sim = 2000
)

# Plot empirical distribution
hist(
  mc_sim$simulations,
  breaks = 40,
  col = "steelblue",
  border = "white",
  main = "Empirical Distribution of DCF Fair Value per Share",
  xlab = "Fair Value per Share (USD)",
  ylab = "Frequency"
)
abline(v = mc_sim$median_fair_value, col = "darkgreen", lwd = 2, lty = 1)
abline(v = mc_sim$value_at_risk_5pct, col = "red", lwd = 2, lty = 2)
abline(v = mc_sim$upside_95pct, col = "blue", lwd = 2, lty = 2)
legend(
  "topright",
  legend = c(
    sprintf("Median: $%.2f", mc_sim$median_fair_value),
    sprintf("5%% VaR: $%.2f", mc_sim$value_at_risk_5pct),
    sprintf("95%% Upside: $%.2f", mc_sim$upside_95pct)
  ),
  col = c("darkgreen", "red", "blue"),
  lty = c(1, 2, 2),
  lwd = 2
)
```

---

# Automated Research Dossier

To run the complete 4-stage autonomous research pipeline directly inside RStudio:

```{r run_pipeline_demo, eval=FALSE}
# Executes Analyst, Verifier, and Skeptic committee pipeline
dossier <- run_agent_pipeline("AAPL", workflow = 1, strict_audit = FALSE)
cat(dossier$final_report)
```

---
*Report generated via Antigravity Finance Agents Committee & RStudio v4.6.1.*
